SatNOGS: Satellite~Networked~Open~Ground~Station

### 2015-08-26 paper.tex
add todo
typo

% TODO: GS idle time

@@

This paper seeks to give an overview of the SatNOGS project major components.
Figure \figref{f:overall} gives a high-level overview of the relationship between users and ground stations.
Figure \figref{modular} and the following sections describe the four major sub-projects: Network, DB, Client, and Ground Station.
The modular approach maximizes use of already available components at a ground station.

>>>>

TODO: ground stations are not locally-used much, 1\% duty cycle.  SatNOGS can use the otherwise idle time.  Like SETI@home, folding@home, etc.

@@

This paper seeks to give an overview of the SatNOGS project major components.
Figure \figref{f:overall} gives a high-level overview of the relationship between users and ground stations.
Figure \figref{f:modular} and the following sections describe the four major sub-projects: Network, DB, Client, and Ground Station.
The modular approach maximizes use of already available components at a ground station.
